\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2020-07-12 doc/USER_MANUAL/14_post_processing.tex
Buildbot ran the code beautifier.
master/slave -> main/secondary after new linux language

You do have further options to change this default output behavior,
given in the main constants file \texttt{constants.h} located in \texttt{src/shared/}
directory:
\begin{description}
\item [{\texttt{SEISMOGRAMS\_BINARY}}] set to \texttt{.true.} to have seismograms
written out in binary format.
\item [{\texttt{WRITE\_SEISMOGRAMS\_BY\_MASTER}}] Set to \texttt{.true.}
to have only the master process writing out seismograms. This can
be useful on a cluster, where only the master process node has access
to the output directory.
\item [{\texttt{USE\_OUTPUT\_FILES\_PATH}}] Set to \texttt{.false.} to
have the seismograms output to \texttt{LOCAL\_PATH} directory specified
in the main parameter file \texttt{DATA/Par\_file}. In this case,
you could collect the synthetics onto the frontend using the \texttt{collect\_seismo\_lsf\_multi.pl}
script located in the \texttt{utils/Cluster/lsf/} directory. The usage
of the script would be e.g.:

>>>>

You do have further options to change this default output behavior,
given in the main constants file \texttt{constants.h} located in \texttt{src/shared/}
directory:
\begin{description}
\item [{\texttt{SEISMOGRAMS\_BINARY}}] set to \texttt{.true.} to have seismograms
written out in binary format.
\item [{\texttt{WRITE\_SEISMOGRAMS\_BY\_MAIN}}] Set to \texttt{.true.}
to have only the main process writing out seismograms. This can
be useful on a cluster, where only the main process node has access
to the output directory.
\item [{\texttt{USE\_OUTPUT\_FILES\_PATH}}] Set to \texttt{.false.} to
have the seismograms output to \texttt{LOCAL\_PATH} directory specified
in the main parameter file \texttt{DATA/Par\_file}. In this case,
you could collect the synthetics onto the frontend using the \texttt{collect\_seismo\_lsf\_multi.pl}
script located in the \texttt{utils/Cluster/lsf/} directory. The usage
of the script would be e.g.:
